### 2025-06-06 paper/results.tex
Update results.

The fixed-state structure of social learning models compounds this challenge. In each episode, agents can only observe and learn from one realized state, forcing them away from the ex ante strategies that theoretical frameworks prescribe. Instead of developing belief-contingent policies, agents learn "do X" during episodes with state A, then encounter conflicting objectives to "do Y" during subsequent episodes with state B.

One natural approach to address this limitation would be to train agents across different environmental configurations, then evaluate their behavior under the full spectrum of possible conditions. However, this approach consistently fails due to a fundamental constraint of neural network learning. When network parameters are continuously updated across episodes, action-value functions adapt to the most recent state, leading to policies that are only optimal for the last state encountered. This phenomenon—known as \emph{catastrophic forgetting}—fundamentally constrains model evaluation for ex ante analysis.

@@

This methodology provides a limited window into multi-agent learning patterns, allowing us to examine whether observed disparities represent structural features that persist across episodes rather than artifacts of specific agent characteristics.

>>>>

The fixed-state structure of social learning models compounds this challenge. In each episode, agents can only observe and learn from one realized state, forcing them away from the ex ante strategies that theoretical frameworks prescribe. Instead of developing belief-contingent policies that are flexible across states, agents learn "do X" during episodes with state A, then encounter conflicting objectives to "do Y" during subsequent episodes with state B.

One natural approach to address this limitation would be to train agents across different environmental configurations, then evaluate their behavior under the full spectrum of possible conditions. However, this approach consistently fails due to a fundamental constraint of neural network learning. When network parameters are continuously updated across episodes with fixed states, action-value functions adapt to the most recent state, leading to policies that are only optimal for the last state encountered. This phenomenon—known as \emph{catastrophic forgetting}—fundamentally constrains model evaluation for ex ante analysis.

@@

This methodology provides a limited window into multi-agent learning patterns, allowing us to examine whether observed disparities represent structural features that persist across episodes rather than artifacts of specific agent characteristics. However, in addition to the fundamental limitations discussed above, it prevents the ability to isolate belief formation mechnanisms from network parameter updates.
